---
title: "Untitled"
format: html
---

```{r}
# Intercept interpretation
exp(0.52950)

exp(0.52950) / (1+exp(0.52950))


```

The predicted odds of an 18 year old white female player's first significant confessional portraying a positive attitude on season 36, before the implementation of diversity rules, are 1.70. The predicted probability is 0.63. 

```{r}
# POC interpretation
exp(-0.47234)

100*exp(-0.47234) - 100
```

```{r}
poc_ci = exp(coef(survivor.lm.2)[2] + c(-1, 1)*qnorm(0.975)*sqrt(vcov(survivor.lm.2)[2, 2]))

poc_ci[1]*100 - 100
poc_ci[2]*100 - 100
```

For players of the same age and gender playing on the same season pre-diversity rule implementation, the predicted odds of a player's first significant confessional portraying a positive attitude are 37.6% lower (95% CI: 76.6% decrease, 66.1% increase) for players of color than white players.

```{r}
# POC * diversity rule interpretation
exp(-0.47234 + 0.35283)

100*exp(-0.47234 + 0.35283) - 100
```

```{r}
poc_div_ci = exp((-0.47234 + 0.35283) + c(-1,1)*qnorm(0.975)*sqrt(vcov(survivor.lm.2)[2,2] + vcov(survivor.lm.2)[15,15] + 2*vcov(survivor.lm.2)[2,15]))

poc_div_ci[1]*100 - 100

poc_div_ci[2]*100 - 100
```

For players of the same age and gender playing on the same season post-diversity rule implementation, the predicted odds of a player's first significant confessional portraying a positive attitude are 11.3% lower (95% CI: 70.4% decrease, 166% increase) for players of color than white players. 

```{r}
# Gender interpretation
exp(0.32090)

100*exp(0.32090) - 100

gender_ci = exp(coef(survivor.lm.2)[5] + c(-1, 1)*qnorm(0.975)*sqrt(vcov(survivor.lm.2)[5, 5]))

100*gender_ci[1] - 100
100*gender_ci[2] - 100
```

For players of the same age and poc status playing on the same season, the predicted odds of a player's first significant confessional portraying a positive attitude are 37.8% higher (95% CI: 31.4% decrease, 177% increase) for male players than female players.

```{r}
# Age interpretation
exp(0.00549)

100*exp(0.00549) - 100
```

```{r}
age_ci = exp(coef(survivor.lm.2)[4] + c(-1, 1)*qnorm(0.975)*sqrt(vcov(survivor.lm.2)[4, 4]))

100*age_ci[1] - 100
100*age_ci[2] - 100
```

For players of the same gender and poc status playing on the same season, a one-year increase in player age is associated with a 0.55% increase (95% CI: 3.49% decrease, 4.76% increase) in the predicted odds of a player's first significant confessional portraying a positive attitude.

```{r}
# Season 37 interpretation
exp(1.21085)

exp(1.21085)*100 - 100
```

For players of the same age, gender, and poc status, the the predicted odds of a player's first significant confessional portraying a positive attitude are 236% higher on season 37 than season 36.

```{r}
# Season 38 interpretation
exp(-0.17742)

exp(-0.17742)*100 - 100
```

For players of the same age, gender, and poc status, the the predicted odds of a player's first significant confessional portraying a positive attitude are 16.3% lower on season 38 than season 36.

```{r}
# Season 39 interpretation
exp(0.29696)

exp(0.29696)*100 - 100
```

For players of the same age, gender, and poc status, the the predicted odds of a player's first significant confessional portraying a positive attitude are 34.6% higher on season 39 than season 36.

```{r}
# Season 40 interpretation
exp(0.28638)

exp(0.28638)*100 - 100
```

For players of the same age, gender, and poc status, the the predicted odds of a player's first significant confessional portraying a positive attitude are 33.2% higher on season 40 than season 36.

```{r}
# Season 41 interpretation
exp(1.39589 -1.50466)

exp(1.39589 -1.50466)*100 - 100
```

For players of the same age, gender, and poc status, the the predicted odds of a player's first significant confessional portraying a positive attitude are 10.3% lower on season 41 than season 45.

```{r}
# Season 42 interpretation
exp(1.39589 -0.83982)

exp(1.39589 -0.83982)*100 - 100
```

For players of the same age, gender, and poc status, the the predicted odds of a player's first significant confessional portraying a positive attitude are 74.4% higher on season 42 than season 45.

```{r}
# Season 43 interpretation
exp(1.39589 -0.81816)

exp(1.39589 -0.81816)*100 - 100
```

For players of the same age, gender, and poc status, the the predicted odds of a player's first significant confessional portraying a positive attitude are 78.2% higher on season 43 than season 45.

```{r}
# Season 44 interpretation
exp(1.39589 -0.04789)

exp(1.39589 -0.04789)*100 - 100
```

For players of the same age, gender, and poc status, the the predicted odds of a player's first significant confessional portraying a positive attitude are 285% higher on season 44 than season 45.

```{r}
# Season 45 interpretation
exp(1.39589)

exp(1.39589)*100 - 100
```

For players of the same age, gender, and poc status, the the predicted odds of a player's first significant confessional portraying a positive attitude are 304% higher on season 45 than season 36.


```{r}
kable(broom::tidy(survivor.lm.2), digits = 2)
```


```{r}
survivor.full = glm(Attitude ~ poc * div_rules + age_adj + gender + season, data = survivor, family = "binomial")
survivor.null = glm(Attitude ~ 1, data = survivor, family = "binomial")
anova(survivor.null, survivor.full, test = "Chisq")
```

```{r}
survivor.full = glm(Attitude ~ poc * div_rules + age_adj + gender + season, data = survivor, family = "binomial")
survivor.minimal = glm(Attitude ~ poc * div_rules + season, data = survivor, family = "binomial")
anova(survivor.minimal, survivor.full, test = "Chisq")
survivor.minimal.age = glm(Attitude ~ poc * div_rules + age_adj + season, data = survivor, family = "binomial")
anova(survivor.minimal.age, survivor.full, test = "Chisq")
survivor.minimal.gender = glm(Attitude ~ poc * div_rules + gender + season, data = survivor, family = "binomial")
anova(survivor.minimal.gender, survivor.full, test = "Chisq")
```

$$logit \{P(Y_i=1|poc,div,age,gender,season)\} = 0.53 - (0.47 \times poc) + (1.40 \times div) + (0.005 \times age)+ (0.32 \times male)$$
$$+ (1.21 \times season37) - (0.18 \times season38) + (0.30 \times season39) + (0.29 \times season40) - (1.50 \times season41)$$
$$-(0.84 \times season42) - (0.82 \times season43) - (0.05 \times season44) + (0.35 \times poc \times div)$$
